---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Overview

<!-- badges: start -->
<!-- badges: end -->

metricpulling reads data from a DEFRA Biodiversity Net Gain metric xlsx file and
does the following actions:

- runs a series of checks for errors or missing data
- creates summaries of baseline and proposed data for all habitat modules (habitat, hedge, watercourse)
- creates sumamries of net units for each habitat module
- creates summaries of the trading rules

These summaries can be used in creating reports on BNG projects.

## Installation

The package can be installed from Digital Ecology’s Codeberg repository:

``` r
remotes::install_git("https://codeberg.org/Digital-Ecology/metric_pulling.git")
```

## Examples

To run the metric checks:

```{r metric-check-example}
library(metricpulling)

metric <- system.file("extdata", "OnSiteBoth.xlsx", package = "metricpulling")

metric_check(metric)

```

To return a data summary for baseline habitats:

```{r habitat-summary-example}

pullonsitehabitatbaseline(metric)

```

## Bugs

If you encounter a bug, please file an issue with a minimal reproducible example on [Codeberg](https://codeberg.org/Digital-Ecology/metric_pulling/issues).

## Code of Conduct

This project is released subject to a [Contributor Code of Conduct](https://www.contributor-covenant.org/version/2/1/code_of_conduct/). By participating in the project you agree to bide by its terms.
